---
title: '**Probability and Statistics with R**'
author: '**Assignment 2**'
date: "Submission Nov 16-2022 (Wednesday)"
output:
  html_document:
    df_print: paged
---

**Note**: Below I explain how you collaborate on `GitHub`.

1. It will be group assignment. 
2. A group would be of size at most 3. If you want to create a group size more than 3, you must take permission.
3. Decide among yourself and one of you create a GitHub repository for Probability Statistics Assignments.
4. In that repository add your group members as collaborator
5. Once you add your collaborator (or group members), create a folder and name it as `Assignment_2`
6. In that folder you should have 2 folders `code` and `report`. And one `README.md` file. Write a brief report in `README.md` file.
7. For each problem, you should create a separate GitHub `issue`. All your discussion should be documented in the `issue`. 
8. In the issue mention clearly, which group member is taking ownership of what problem?
9. The other member should `fork` the repository in their GitHub account.
10. Once you have your forked the main repository in your GitHub account - you should clone the repository in you local laptop or just download it as zip.
11. Once you develop the code - you should `commit` the code first in your repository and then `push` it.
12. Finally you make the `pull-request` in the final repository.
13. Once a member make a pull request, the other members have to review the code.
14. While reviewing the code the reviewer may have to download the code and run the code in his or her system and reproduce the result.
15. If the result is reproduced then she or he would accept and merge the code in final repository.
16. At the end you submit the link of the repository in the moodle.
17. The entire process will be evaluated.

## Problem 1

Suppose $X$ denote the number of goals scored by home team in premier league. We can assume $X$ is a random variable. Then we have to build the probability distribution to model the probability of number of goals. Since $X$ takes value in $\mathbb{N}=\{0,1,2,\cdots\}$, we can consider the geometric progression sequence as possible candidate model, i.e.,
$$
S=\{a,ar,ar^2,ar^{3},\cdots\}.
$$
But we have to be careful and put proper conditions in place and modify $S$ in such a way so that it becomes proper probability distributions. 

1. Figure out the necesary conditions and define the probability distribution model using $S$.
2. Check if mean and variance exists for the probability model. 
3. Can you find the analytically expression of mean and variance.
4. From historical data we found the following summary statistics
\begin{table}[ht]
\centering
     \begin{tabular}{c|c|c|c}\hline
     mean &  median & variance & total number of matches\\ \hline
     1.5 & 1 & 2.25 & 380\\ \hline
     \end{tabular}
\end{table}
Using the summary statistics and your newly defined probability distribution model find the following:
 a. What is the probability that home team will score at least one goal?
 b. What is the probability that home team will score at least one goal but less than four goal?

5. Suppose on another thought you want to model it with off-the shelf Poisson probability models. Under the assumption that underlying distribution is Poisson probability find the above probabilities, i.e.,
 a. What is the probability that home team will score at least one goal?
 b. What is the probability that home team will score at least one goal but less than four goal?
6. Which probability model you would prefer over another?
7. Write down the likelihood functions of your newly defined probability models and Poisson models. Clearly mention all the assumptions that you are making.


1.We are modelling the number of goals scored by the home team in a premier league match using S the geometric progression sequence.We have made the following conditions and definitions regarding the model.
 Let $a$ to associated with an hypothetical situation after which no goal is going to be scored and $r$ that a goal happens.We assume $r>0$ and $a>0$
 For example: consider outcome of a match to be $ra$, this means that in that match after the home team scored a goal it didn't score any more goals.The outcome only $a$ would represent no goal was scored in the match by the home team.
 The distribution would be 
 
$$
 f(X=n)= r^na
$$
 
 For every $n$ the the value is positive.For this to be a probability function sum of all the probabilities should be 1.
 
$$
\sum_{n=0}^{inf} f(X=n)=1 \\
  \sum_{n=0}^{inf} r^na=1 \\
  a\sum_{n=0}^{inf} r^n=1 \\
$$
 
This series converges only when $|r|<1$. Therefore we have $0<r<1$ (associated to probability of scoring a goal)
$$
\frac{a}{1-r} =1 \\
a=1-r
$$
Therefore the probability distribution would be
$$
 P(X=n)= r^n(1-r)~~~~~n=0,1,2,\cdots\
$$
where n is the number of goals scored by the home team in that match.

2. We need to show that mean and variance exists for the new distribution we have defined.To show mean exists we need to show that $E[|X|]$ exist, since $X$ takes positive values E[|X|] is nothing but E[X].
$$
E[X]= \sum_{n=0}^{inf} nP(X=n) \\
 = \sum_{n=0}^{inf} nr^n(1-r)\\
 = (1-r)\sum_{n=0}^{inf} nr^n \\
 (~~wkt~~~~ \sum_{n=0}^{inf} nr^n =\frac {r}{(1-r)^2}~~) \\
 = (1-r)\frac {r}{(1-r)^2}= \frac {r}{(1-r)} \\
$$
Therefore mean exists for the new distribution, we can similarly show that $E[|X^{2}|]$ (which is equal to the E[X^{2}]) exists and is equal to 
$$
E[X^{2}]= \frac {r^{2} + r}{(1-r)^{2}}
$$
Hence variance also exists as 
$$
var[X]=E[X^{2}]-(E[X])^{2}
$$
and it is equal to
$$
Var[X]= \frac {r^{2} + r}{(1-r)^{2}} ~-~  (\frac {r}{(1-r)})^{2} \\
= ~~~~ \frac {r}{(1-r)^{2}}
$$
Therefore mean and variance exists for the new distribution.
3. The analytical form of mean and variance is
$$
E[X]=\frac {r}{(1-r)} ~~~~  Var[X]=\frac {r}{(1-r)^{2}}
$$
4. Historical data gives us that the mean number of goals scored by the home team (based on past 380 matches ) is 1.5. We equate this to our theoretical mean and calculate the value.
$$
\frac {r}{1-r}=\frac {3}{2} \\
2r=3-3r \\
r=\frac {3}{5}
$$
Therefore our probability distribution is 
$$
P(X=n)=\frac {2}{5}(\frac {3}{5})^{n}
$$
4.
a. Probability of at least one goal.
$$
P(X \geq 1)= \sum_{n=1}^{inf} \frac {2}{5}(\frac {3}{5})^{n}\\
= \frac {2}{5} \sum_{n=1}^{inf} (\frac {3}{5})^{n}
= \frac {2}{5} \frac {\frac {3}{5}}{1-\frac {3}{5}} = \frac {3}{5} 
$$

This is similar to $ 1- P(X=0) = 1- \frac {2}{5} = \frac{3}{5} $
b. The probability that home team will score at least one goal but less than four goal
$$
P(1\leq X < 4)= \sum_{n=1}^{3} \frac {2}{5}(\frac {3}{5})^{n}\\
= \frac {2}{5} \sum_{n=1}^{3} (\frac {3}{5})^{n}
= \frac {2}{5}( \frac {3}{5} + \frac {9}{25}+ \frac {27}{125}) = 0.4704  
$$
We know that this new model is geometric distribution with parameter $p=\frac {3}{5}$. We can use inbuilt functions to calculate these probabilities.
```{r message=FALSE, warning=FALSE}
## a. probability of atleast one goal
P_a= 1- dgeom(0,2/5)
## a. probability of atleast one goal and less than 4 goals
P_b= sum(dgeom(c(1,2,3),2/5))
P_a
P_b
```
5. We assume that the underlying distribution for the number of goals scored by the home team is poisson distribution.Let random variable $Y \sim Pois(\lambda)$. We know that $E[Y]=\lambda$ and from historical data we know the mean is 1.5. Hence $Y \sim Pois(\lambda=1.5)$. We calculate the probability using inbuilt function.
```{r message=FALSE, warning=FALSE}
## a. probability of at least one goal
P_a= 1- dpois(0,1.5)

## b. probability of at least one goal and less than 4 goals
P_b= sum(dpois(c(1,2,3),1.5))


P_a
P_b
```
6. We would expect the poisson distribution to be better as the concept of counting certain event in a fixed amount of time fits better in poisson distribution than in a geometric setting. (Ex. Poisson distribution is used to model number of cars passing the tollgate etc).We would expect poisson to be better for counting the number of goals but we know that for poisson distribution, mean and variance should be equal, in our case mean=1.5 and variance=2.25. Hence poisson is not a good fit and we would prefer the new geometric distribution that we defined.  

7. Maximum Likelihood function: 
Consider $x_1,x_2 \cdots ,x_n$ be a sample drawn from the theoretical distribution
  a. New distribution - $P(X=n)=(1-r)(r)^{n}$
  The likelihood function for the following distribution is :-
$$
L(r_\theta|x_1,x_2 \cdots ,x_n)=P(x_1,x_2 \cdots ,x_n|r_\theta)\\
=P(x_1|r_\theta).P(x_2|r_\theta) \cdots P(x_n|r_\theta) \\
=(1-r_\theta)(r_\theta)^{x_1}.(1-r_\theta)(r_\theta)^{x_1} \cdots (1-r_\theta)(r_\theta)^{x_n}\\
=(1-r_\theta)^{n}.(r_\theta)^{\sum_{i=1}^{n} x_i}
$$
  b. Poisson Distribution - $P(X=n)=\frac {e^{-\lambda} \lambda^n}{n!}$
  The likelihood function of the following distribution is 
$$
L(\lambda_\theta|x_1,x_2 \cdots ,x_n)=P(x_1,x_2 \cdots ,x_n|\lambda_\theta)\\
=P(x_1|\lambda_\theta).P(x_2|\lambda_\theta) \cdots P(x_n|\lambda_\theta) \\
=\frac {e^{-\lambda} \lambda^{x_1}}{x_1!}.\frac {e^{-\lambda} \lambda^{x_2}}{x_2!} \cdots \frac {e^{-\lambda} \lambda^{x_n}}{x_n!}\\
= \frac {e^{-n\lambda} \lambda^{\sum_{i=1}^{n} x_i}}{x_1!.x_2! \cdots x_n! }
$$
One main assumption that we make in both the likelihood functions is that the sample is independently and identically drawn from their respective distributions. Here independence means that the goals scored in one match doesn't affect the goals scored in another match. We assume that each match is identical to the other matches (that is there is no knockout matches or a club rivalry match), this ensures that the distribution followed in each match is identical.




## Problem 2 : Simulation Study to Understand Sampling Distribution

**Part A**
Suppose $X_1,X_2,\cdots,X_n\stackrel{iid}{\sim} Gamma(\alpha,\sigma)$, with pdf as
$$
f(x | \alpha,\sigma)=\frac{1}{\sigma^{\alpha}\Gamma(\alpha)}e^{- x/\sigma}x^{\alpha-1},~~~~0<x<\infty,
$$
The mean and variance are $E(X)=\alpha\sigma$ and $Var(X)=\alpha\sigma^2$. Note that `shape = ` $\alpha$ and `scale = ` $\sigma$.

1. Write a `function` in `R` which will compute the MLE of $\theta=\log(\alpha)$ using `optim` function in `R`. You can name it `MyMLE`
2. Choose `n=20`, and `alpha=1.5` and `sigma=2.2`
     (i) Simulate $\{X_1,X_2,\cdots,X_n\}$ from `rgamma(n=20,shape=1.5,scale=2.2)`
     (ii) Apply the `MyMLE` to estimate $\theta$ and append the value in a vector
     (iii) Repeat the step (i) and (ii) 1000 times
     (iv) Draw histogram of the estimated MLEs of $\theta$.
     (v) Draw a vertical line using `abline` function at the true value of $\theta$.
     (vi) Use `quantile` function on estimated $\theta$'s to find the 2.5 and 97.5-percentile points. 
3.  Choose `n=40`, and `alpha=1.5` and repeat the (2).
4.  Choose `n=100`, and `alpha=1.5` and repeat the (2).
5. Check if the gap between 2.5 and 97.5-percentile points are shrinking as sample size `n` is increasing?

*Hint*: Perhaps you should think of writing a single `function` where you will provide the values of `n`, `sim_size`, `alpha` and `sigma`; and it will return the desired output. 

```{r,warning=FALSE,message=FALSE}
MyMLE = function(data_obtained,sigma,initial)
{
  NegLogLike = function(initial,data_obtained)
  {
    alphatemp = exp(initial)
    n = length(data_obtained)
    logl = 0
    for(i in 1:n)
    {
      logl = logl + dgamma(data_obtained[i],
                  shape = alphatemp,scale=sigma,log = TRUE)
      
    }
    return(-logl)
  }
  fit = optim(initial,NegLogLike,data_obtained=data_obtained)
  log(exp(fit$par))
}

resultfunction = function(alpha,sigma,n,sim_size,initial)
{
  mles = c(rep(0,sim_size))
  for(i in 1:sim_size)
  {
    dat = rgamma(n,shape=alpha,scale = sigma)
    mles[i] = MyMLE(data_obtained = dat,sigma = sigma,
                    initial = initial)
  }
  library(ggplot2)
  library(randomcoloR) 
  hist(mles,col=randomColor(),main='Histogram for MLES ')
  abline(v=log(alpha),lwd=2,col='black')
  quantile(mles,probs=0.975) - quantile(mles,probs=0.025)
}

```
<br><br><br>
We have now written a function called 'resultfunction which takes values for alpha, sigma, n, simulation size and initial value for all mle estimates as the input and gives the desired output.
<br><br><br>
```{r}

resultfunction(alpha = 1.5,sigma = 2.2,initial = 3,
              n = 20,sim_size = 1000)
resultfunction(alpha = 1.5,sigma = 2.2,initial = 3,
              n = 40,sim_size = 1000)
resultfunction(alpha = 1.5,sigma = 2.2,initial = 3,
              n = 100,sim_size = 1000)


```

\newpage

## Problem 3: Analysis of `faithful` datasets.

Consider the `faithful` datasets:
```{r}
attach(faithful)
hist(faithful$waiting,xlab = 'waiting',probability = T,col='pink',main='')
```

Fit following three models using MLE method and calculate **Akaike information criterion** (aka., AIC) for each fitted model. Based on AIC decides which model is the best model? Based on the best model calculate the following probability
$$
\mathbb{P}(60<\texttt{waiting}<70)
$$

(i) **Model 1**:
$$
f(x)=p*Gamma(x|\alpha,\sigma_1)+(1-p)N(x|\mu,\sigma_2^2),~~0<p<1
$$

(ii) **Model 2**:
$$
f(x)=p*Gamma(x|\alpha_1,\sigma_1)+(1-p)Gamma(x|\alpha_2,\sigma_2),~~0<p<1
$$

(iii) **Model 3**:
$$
f(x)=p*logNormal(x|\mu_1,\sigma_1^2)+(1-p)logNormal(x|\mu_1,\sigma_1^2),~~0<p<1
$$

\newpage

## Problem 4: Modelling Insurance Claims

Consider the `Insurance` datasets in the `MASS` package. The data given in data frame `Insurance` consist of the numbers of policyholders of an insurance company who were exposed to risk, and the numbers of car insurance claims made by those policyholders in the third quarter of 1973.

This data frame contains the following columns:

`District` (factor): district of residence of policyholder (1 to 4): 4 is major cities.

`Group` (an ordered factor): group of car with levels <1 litre, 1–1.5 litre, 1.5–2 litre, >2 litre.

`Age` (an ordered factor): the age of the insured in 4 groups labelled <25, 25–29, 30–35, >35.

`Holders` : numbers of policyholders.

`Claims` : numbers of claims

```{r}
library(MASS)
plot(Insurance$Holders,Insurance$Claims
     ,xlab = 'Holders',ylab='Claims',pch=20)
grid()
```

**Note**: If you use built-in function like `lm` or any packages then no points will be awarded.

**Part A**: We want to predict the `Claims` as function of `Holders`. So we want to fit the following models:
$$
\texttt{Claims}_i=\beta_0 + \beta_1~\texttt{Holders}_i + \varepsilon_i,~~~i=1,2,\cdots,n
$$
*Assume* : $\varepsilon_i\sim N(0,\sigma^2)$. Note that $\beta_0,\beta_1 \in\mathbb{R}$ and $\sigma \in \mathbb{R}^{+}$.

The above model can alse be re-expressed as,
$$
\texttt{Claims}_i\sim N(\mu_i,\sigma^2),~~where
$$
$$
\mu_i =\beta_0 + \beta_1~\texttt{Holders}_i + \varepsilon_i,~~~i=1,2,\cdots,n
$$


(i) Clearly write down the negative-log-likelihood function in `R`. Then use `optim` function to estimate MLE of $\theta=(\beta_0,\beta_1,\sigma)$
(ii) Calculate **Bayesian Information Criterion** (BIC) for the model.

**Part B**: Now we want to fit the same model with change in distribution:
$$
\texttt{Claims}_i=\beta_0 + \beta_1~\texttt{Holders}_i + \varepsilon_i,~~~i=1,2,\cdots,n
$$
  Assume : $\varepsilon_i\sim Laplace(0,\sigma^2)$. Note that $\beta_0,\beta_1 \in\mathbb{R}$ and $\sigma \in \mathbb{R}^{+}$.

(i) Clearly write down the negative-log-likelihood function in `R`. Then use `optim` function to estimate MLE of $\theta=(\beta_0,\beta_1,\sigma)$

(ii) Calculate **Bayesian Information Criterion** (BIC) for the model.

**Part C**: We want to fit the following models:
$$
\texttt{Claims}_i\sim LogNormal(\mu_i,\sigma^2), where
$$
$$
\mu_i=\beta_0 + \beta_1 \log(\texttt{Holders}_i), ~~i=1,2,...,n
$$

Note that $\beta_0,\beta_1 \in\mathbb{R}$ and $\sigma \in \mathbb{R}^{+}$.

(i) Clearly write down the negative-log-likelihood function in `R`. Then use `optim` function to estimate MLE of $\theta=(\alpha,\beta,\sigma)$

(ii) Calculate **Bayesian Information Criterion** (BIC) for the model.

**Part D**: We want to fit the following models:
$$
\texttt{Claims}_i\sim Gamma(\alpha_i,\sigma), where
$$
$$
log(\alpha_i)=\beta_0 + \beta_1 \log(\texttt{Holders}_i), ~~i=1,2,...,n
$$



(iii) Compare the BIC of all three models

## Problem 5: Computational Finance - Modelling Stock prices

Following piece of code download the prices of TCS since 2007

```{r}
library(quantmod)
getSymbols('TCS.NS')
tail(TCS.NS)
```
Plot the adjusted close prices of TCS
```{r}
plot(TCS.NS$TCS.NS.Adjusted)
```

**Download the data of market index Nifty50**. The Nifty 50 index indicates how the over all market has done over the similar period.
```{r}
getSymbols('^NSEI')
tail(NSEI)
```
Plot the adjusted close value of Nifty50
```{r}
plot(NSEI$NSEI.Adjusted)
```


### Log-Return 
We calculate the daily log-return, where log-return is defined as
$$
r_t=\log(P_t)-\log(P_{t-1})=\Delta \log(P_t),
$$
where $P_t$ is the closing price of the stock on $t^{th}$ day.

```{r}
TCS_rt = diff(log(TCS.NS$TCS.NS.Adjusted))
Nifty_rt = diff(log(NSEI$NSEI.Adjusted))
retrn = cbind.xts(TCS_rt,Nifty_rt) 
retrn = na.omit(data.frame(retrn))

plot(retrn$NSEI.Adjusted,retrn$TCS.NS.Adjusted
     ,pch=20
     ,xlab='Market Return'
     ,ylab='TCS Return'
     ,xlim=c(-0.18,0.18)
     ,ylim=c(-0.18,0.18))
grid(col='grey',lty=1)
```

+ Consider the following model:

$$
r_{t}^{TCS}=\alpha + \beta r_{t}^{Nifty} + \varepsilon,
$$
where $\mathbb{E}(\varepsilon)=0$ and $\mathbb{V}ar(\varepsilon)=\sigma^2$.
1. Estimate the parameters of the models $\theta=(\alpha,\beta,\sigma)$ using the method of moments type plug-in estimator discussed in the class.
$$
\\\ \\ 
$$
The three population moments that we are going to use to estimate the parameter values are 
$$
E[\epsilon_i]=0 ~~~ E[\epsilon_i r_{t_i}^{Nifty} ]=0 ~~~ E[\epsilon_i^{2}]=\sigma^{2} \\\ \\
$$

The equivalent sample moments for the above population moments are:-  

$$
\frac {1}{n} \sum_{i=1}^{n} [r_{t_i}^{TCS}-\hat\alpha - \hat\beta r_{t_i}^{Nifty}]=0 ~~~\\
\frac {1}{n} \sum_{i=1}^{n} r_{t_i}^{TCS}- \frac {1}{n} \sum_{i=1}^{n}\hat\alpha - \frac {1}{n} \sum_{i=1}^{n}\hat\beta r_{t_i}^{Nifty}=0 ~~~\\
\overline r_{t_i}^{TCS}-\hat\alpha - \hat\beta \overline r_{t_i}^{Nifty} =0 ~~~~~~---- equation~1\\\ \\
\frac {1}{n} \sum_{i=1}^{n} [(r_{t_i}^{TCS}-\hat\alpha - \hat\beta r_{t_i}^{Nifty})r_{t_i}^{Nifty}]=0 \\
\frac {1}{n} \sum_{i=1}^{n} [(r_{t_i}^{TCS}r_{t_i}^{Nifty}-\hat\alpha r_{t_i}^{Nifty} - \hat\beta (r_{t_i}^{Nifty})^{2}]=0 \\
\frac {1}{n} \sum_{i=1}^{n} (r_{t_i}^{TCS}r_{t_i}^{Nifty}- \frac {1}{n} \sum_{i=1}^{n} \hat\alpha r_{t_i}^{Nifty} - \frac {1}{n} \sum_{i=1}^{n}  \hat\beta (r_{t_i}^{Nifty})^{2}=0 \\
\frac {1}{n} \sum_{i=1}^{n} (r_{t_i}^{TCS}r_{t_i}^{Nifty})-  \hat\alpha \overline r_{t_i}^{Nifty} - \hat\beta \frac {1}{n} \sum_{i=1}^{n}   (r_{t_i}^{Nifty})^{2}=0 ~~~~~~---- equation~2\\\ \\ 
\frac {1}{n} \sum_{i=1}^{n} [r_{t_i}^{TCS}-\hat\alpha - \hat\beta r_{t_i}^{Nifty}]^{2}=\hat\sigma^{2}~~~~~~---- equation~3
$$



```{r message=FALSE, warning=FALSE}
tcs_avg=mean(retrn$TCS.NS.Adjusted)
nifty_avg=mean(retrn$NSEI.Adjusted)
tcsxnifty_avg=mean(retrn$TCS.NS.Adjusted*retrn$NSEI.Adjusted)
sqr_nifty_avg=mean(retrn$NSEI.Adjusted^{2})

## the equations are 
## 1. tcs_avg - \hat\alpha -\hat\beta*nifty_avg=0
## 2. tcsxnifty_avg - \hat\alpha*nifty_avg - \hat\beta*sqr_nifty_avg =0

A=matrix(c(-1,-nifty_avg,-nifty_avg,-sqr_nifty_avg),2,2)
b=c(-tcs_avg,-tcsxnifty_avg)
s=solve(A,b)

si= sum((retrn$TCS.NS.Adjusted - s[1] - s[2]*retrn$NSEI.Adjusted)^2)/(length(retrn$TCS.NS.Adjusted)-2)
```
The estimated values of $\hat\alpha$,$\hat\beta$ and $\sigma^{2}$ respectively is
```{r message=FALSE, warning=FALSE}
c(s,si)
```
2. Estimate the parameters using the `lm` built-in function of `R`. Note that `lm` using the OLS method.
```{r message=FALSE, warning=FALSE}
model_fit=lm(retrn$TCS.NS.Adjusted~retrn$NSEI.Adjusted)
model_fit
```
Therefore the linear model fit is
$$
r_{t}^{TCS}=0.0004611 + 0.7436969 r_{t}^{Nifty}
$$
```{r message=FALSE, warning=FALSE}
tcs_exp=model_fit$coefficients[1] + model_fit$coefficients[2] *retrn$NSEI.Adjusted
si_e=sum((retrn$TCS.NS.Adjusted-tcs_exp)^2)/(length(tcs_exp)-2)
```
The estimated parameter values are 
```{r message=FALSE, warning=FALSE}
c(model_fit$coefficients[1],model_fit$coefficients[2],si_e)
```

3. Fill-up the following table

Parameters | Method of Moments | OLS
-----------|-------------------|-----
$\alpha$   |   0.0004611207    | 0.0004611207
$\beta$    |   0.7436969330    | 0.7436969330
$\sigma$   |   0.0002620749    | 0.0002620749

We got the same estimated parameter values using Method of Moments and the $lm()$ function which uses Ordinary least sqaure method.

4. If the current value of Nifty is 18000 and it goes up to 18200. The current value of TCS is Rs. 3200/-. How much you can expect TCS price to go up?

First we calculate the log returns for nifty and substitute it in the model we fit
```{r message=FALSE, warning=FALSE}
r_nifty=log(18200)-log(18000)
r_tcs=0.0004611207+ 0.7436969330* r_nifty
tcs_in= exp(r_tcs)*3200
tcs_in
```
Therefore we can expect the TCS price to go up 27.893 Rupees.
